Make any stupid plot you want

### 2020-11-23 draft/sections/math.tex
start of fibers

\subsubsection{Fiber Space $F$}
The fibers encode the set of all possible values each observation can take. 
Spivak's \cite{spivakSIMPLICIALDATABASES} formulation of the fibers as a union of named types gives a way to separate the values in the fiber by type:

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$ 
\begin{tikzcd}
    A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
    A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) 
\end{tikzcd}

>>>>

\subsubsection{Fiber Space $F$}
The fibers encode the set of all possible values each observation can take.  Spivak's formulation is that the fibers encode the union of the types of measurements\cite{spivakSIMPLICIALDATABASES}. For example, given the section $\Gamma(mobuis strip) =
\{\sigma_1=\sin, \sigma_2=\cos\}$:
%%fill in more spivak
the fiber $F = \{float, float\}$.

%%% mapping from measurement back to type is the basis for gaurateening invariance

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
Two artists are equivalent when given data containers $\Gamma(E)$ of the same type, they output the same type of prerender $\Gamma(S)$:
\begin{equation}
    \begin{tikzcd}
        A_{\tau_2}: \arrow[d, shift right=2] & \Gamma(E) \arrow[r] & \Gamma(H) &                                                \\
        A_{\tau_1}: \arrow[u, shift right]   & \Gamma(E) \arrow[r] & \Gamma(H) 
    \end{tikzcd}
\end{equation}
